\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{array}
\usepackage{xcolor}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}
\pagestyle{empty}

\begin{document}

%==================== HEADER ====================%
\begin{center}
    {\LARGE \textbf{Krishiv Patel}} \\
    Mumbai, Maharashtra, India \\
    \href{mailto:krishivpatel2326@gmail.com}{krishivpatel2326@gmail.com} $|$ +91-9168669470 \\
    \href{https://www.linkedin.com/in/krishivpatel29}{LinkedIn} $|$ 
    \href{https://github.com/geekykrishiv}{GitHub}
\end{center}

%==================== EDUCATION ====================%
\section*{Education}
\textbf{K J Somaiya Institute of Technology, Mumbai} \hfill 2023 -- 2027 \\
Bachelor of Technology in Computer Engineering \\
CGPA: 9.23 / 10 (Semester 5)

%==================== SKILLS ====================%
\section*{Skills}
\textbf{Languages:} Python, Java, JavaScript, TypeScript, SQL, HTML, CSS \\
\textbf{Frameworks \& Libraries:} React, FastAPI, Node.js, Pandas, NumPy, SciPy, Matplotlib, OpenCV, MediaPipe, PyTorch, TensorFlow, SQLAlchemy, Framer Motion, Recharts \\
\textbf{Tools \& Platforms:} Git, GitHub, Jupyter Notebook, Google Apps Script, WebSockets, JWT, REST APIs, Prompt Engineering, Vite \\
\textbf{Concepts:} Machine Learning, Computer Vision, Statistical Modeling (MLR, MLE, T-tests), DSA, OOP, Signal Processing, Dynamic Programming \\
\textbf{Soft Skills:} Problem Solving, Analytical Thinking, Team Collaboration, Leadership, Communication, Time Management

%==================== PROJECTS ====================%
\section*{Projects}

\textbf{Drum Vision - Gesture-Based Virtual Drum Kit} \hfill \href{https://drum-vision.vercel.app/}{Project Link} \\
\textit{Python, OpenCV, MediaPipe, NumPy}
\begin{itemize}
    \item Developed real-time strike-based gesture detection using motion velocity and direction, enabling accurate drum triggering without static hit zones.
    \item Engineered gesture classification and drum-triggering logic fully decoupled from the frontend, improving modularity and testability.
    \item Optimized the CV pipeline to minimize false positives and maximize responsiveness; won IEEE Poster Competition and Navriti Project Competition.
\end{itemize}

\textbf{SplitEase - Smart Expense Sharing with Analytics} \\
\textit{React 19, Vite, Framer Motion, Recharts, Python, FastAPI, SQLAlchemy, SQLite, WebSockets, NumPy, SciPy, JWT, bcrypt}
\begin{itemize}
    \item Engineered a full-stack expense-sharing platform with a smart debt-simplification algorithm, exact/percentage split validations, and real-time WebSocket synchronization.
    \item Developed an advanced statistical analytics engine implementing MLR, MLE, and T-tests to forecast spending trends and generate quantitative financial insights.
    \item Designed an iOS-inspired frontend with micro-animations; integrated an AI-driven expense categorizer and multi-user CSV exports.
    \item Implemented secure multi-user authentication using JWT and bcrypt with role-based access control.
\end{itemize}

\textbf{Caliber Engineer - Landing Page and Contact Automation} \hfill \href{https://www.caliberengineer.com}{Website} \\
\textit{HTML, CSS, JavaScript, Google Apps Script}
\begin{itemize}
    \item Developed a production-ready landing page for an engineering services company with automated contact form workflows.
    \item Implemented automated email notifications to multiple stakeholders on form submission using Google Apps Script.
    \item Delivered a fully responsive, cross-browser-compatible website establishing a professional online presence.
\end{itemize}

\textbf{AI Gesture-Controlled Audio System} \\
\textit{Python, Machine Learning, NumPy}
\begin{itemize}
    \item Developed a gesture recognition system classifying hand movements in real time to dynamically trigger audio playback using ML models.
    \item Applied ML-based classification to real-time gesture input with focus on accuracy, responsiveness, and usability.
    \item Integrated gesture recognition module with audio control logic for a seamless end-to-end pipeline.
\end{itemize}

\textbf{Machine Learning Experiments and Prototyping} \\
\textit{Python, Pandas, NumPy, Matplotlib, scikit-learn, Jupyter Notebook}
\begin{itemize}
    \item Conducted hands-on ML experiments covering data preprocessing, model training, evaluation, and visualization.
    \item Performed data analysis and feature engineering using Pandas and NumPy for robust model inputs.
    \item Experimented with multiple ML models and workflows; visualized performance metrics using Matplotlib.
\end{itemize}

%==================== ACHIEVEMENTS ====================%
\section*{Achievements}
\begin{itemize}
    \item \textbf{Winner - IEEE Poster Competition (2024):} First place for Drum Vision, recognized for innovation in computer vision and real-time HCI.
    \item \textbf{Winner - Navriti Project Competition (2024):} First place at university-level competition for Drum Vision's technical innovation.
\end{itemize}

%==================== LEADERSHIP ====================%
\section*{Leadership and Extracurricular}

\textbf{Vice President and Lead Guitarist - Pause The Music Club, KJSIT} \hfill 2024 -- Present
\begin{itemize}
    \item Led core leadership team to plan and execute club events and performances.
    \item Performed as lead guitarist at college events.
\end{itemize}

\textbf{Vice Chairperson - AURA Magazine, KJSIT} \hfill 2024 -- Present
\begin{itemize}
    \item Coordinated editorial and design teams for smooth publication workflows.
    \item Supported outreach, coordination, and cross-team communication.
\end{itemize}

\end{document}
